\bf Model Visualization Techniques for a Social Network Model

### 2018-07-11 paper.Rnw
ugh get this done

\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
%---------------------------------------------------
%                 Editing Commands
\newcommand{\hh}[1]{{\color{magenta} #1}}
\newcommand{\st}[1]{{\color{orange} #1}}

@@

\bigskip
\begin{abstract}
Social networks have been studied for decades, beginning with a few foundational works, including the 1967 study, ``The Small World Problem" by Stanley Milgram. In this paper, we concentrate on one type of model for dynamic social networks: the stochastic actor-oriented models (SAOMs), introduced by Snijders (1996). Unlike other network models, SAOMs are not very well understood. We use model visualization techniques introduced in Wickham et al (2015) in order to make them a little less murky. The SAOMs are a prime example of a set of models that can benefit greatly from application of model visualization. With the help of static and dynamic visualizations, we bring the hidden model fitting processes into the foreground, eventually leading to a better understanding and higher accessibility of stochastic actor-oriented models for social network analysts.
\end{abstract}

>>>>

\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
%---------------------------------------------------
%                 Editing Commands
%\newcommand{\hh}[1]{{\color{magenta} #1}}
%\newcommand{\st}[1]{{\color{orange} #1}}

@@

\bigskip
\begin{abstract}
Stochastic actor-oriented models, first introduced by Snijders (1996), are a type of statistical network model for dynamic social networks. Unlike other network models, SAOMs are not very well understood. We use model visualization techniques introduced in Wickham et al (2015) in order to make them a little less murky. The SAOMs are a prime example of a set of models that can benefit greatly from application of model visualization. With the help of static and dynamic visualizations, we bring the hidden model fitting processes into the foreground, eventually leading to a better understanding and higher accessibility of stochastic actor-oriented models for social network analysts.
\end{abstract}
